Import_Map

### 2024-05-28 Code/Import_MapMireillePro.Rmd
changed filename for save.

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_MapComboMireillePro_2",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
```

>>>>

```{r save plot}
ggsave(file = file.path(FigPath, paste("MapComboPro",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
```
